Verification of OpenSSL's SHA3 Keccak function using the Software Analysis Workbench

### 2021-11-22 paper/proof.tex
Add outline

\section{Proof Approach}\label{sec:proof}

>>>>

SHA 3 Details
\begin{compactitem}
  \item Process 1600 bits at a time: $5 * 5 * 64$
  \item State vector is $5*5*64*$
  \item Incoming message padded out to whole number of 1600 bit bit-strings
  \item Processed in order by \texttt{KECCAK}
  \item Keccak turns each block into a state vector (rearranges bit layout in memory)
  \item Keccak has 24 rounds for state vector. 
  \item There are 5 hash functions sequentially applied in each round to iteratively update the state vector
  \item After the last round, keccak turns the state vector back into the bit-string./\item The next unprocessed block is \emph{sponged} (e.g., absorbed) into the current bit-string from the latest keccak and the process is repeated 
  \item The max digest (hash) size is 512 bits in the standard
  \item The final bit-string from keccak after sponging and processing every block in the original message is truncated to the desired digest size 
\end{compactitem}

SAW Details
\begin{compactitem}
  \item Cryptol is a specification language specifically for defining crypto-primitives
  \item It has a compiler to turn Cryptol to SAW core terms
  \item It has an execution environment to run test vectors on specifications
  \item SAW is a tool to prove equivalence between SAW core terms
  \item It uses symbolic execution and must unroll every loop to a fixed length
  \item It can take as input C and Java code and compile those to core terms
  \item It can use overides to replace C and Java code in the term
\end{compactitem}
